\pkg{systemfit}: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-12-27 paper/trunk/systemfit_restrictions.tex
several corrections and a few small improvements
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@901 591db2bd-e0a0-4d22-8c19-2192dbb7da31
changed transpose symbol: ' -> ^\top
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@913 591db2bd-e0a0-4d22-8c19-2192dbb7da31
when referring to equations, we now always use "Equation~\ref{}"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@914 591db2bd-e0a0-4d22-8c19-2192dbb7da31

If the first method (equation~\ref{eq:T-restr}) is chosen
to estimate the coefficients under these restrictions,
the matrix of regressors $X$ is (post-)\hspace{0pt}multiplied
by the $M$ matrix,
so that
\begin{equation}
    X^M = X \cdot M .
\end{equation}
Then, $X^M$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(equations~\ref{eq:ols-wls-sur}--\ref{eq:3slsEViews}).
This results in the linear independent coefficient estimates $\bHat^M$ and
their covariance matrix.
The original coefficients can be obtained by equation (\ref{eq:T-restr})
and the estimated covariance matrix of the original coefficients
can be obtained by
\begin{equation}
   \COVHat \left[ \bHat \right]
   = M \cdot \COVHat \left[ \bHat^M \right] \cdot M' .
\end{equation}

The implementation of the second method to estimate the coefficients
under linear restrictions (equation~\ref{eq:restr-R})
is described for each estimation method in the following sections.

@@

The OLS, WLS, and SUR estimators restricted by $R \beta^R = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{SUR} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' \OHat^{-1} X & R' \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' \OHat^{-1} y \\ q
   \end{array} \right] ,
   \label{eq:ols-wls-sur-r}
\end{equation}
where $\lambda$ is a vector of the Lagrangean multipliers of the restrictions
and $\OHat$ is defined as in section~\ref{sec:Estimation-ols-wls-sur}.
An estimator of the covariance matrix of the estimated coefficients is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R_{SUR} \\[0.2em] \lHat
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \OHat^{-1} X & R' \\
      R & 0
   \end{array} \right]^{-1} .
   \label{eq:cov-ols-wls-sur-r}
\end{equation}

@@

The 2SLS, W2SLS, and standard 3SLS estimators
restricted by $R \beta^R = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{3SLS} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \XHat' \OHat^{-1} \XHat & R' \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \XHat' \OHat^{-1} y \\ q
   \end{array} \right] ,
   \label{eq:2sls-w2sls-3sls-r}
\end{equation}
where $\OHat$ is defined as in section~\ref{sec:Estimation-2sls-w2sls-3sls}.
An estimator of the covariance matrix of the estimated coefficients is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R_{3SLS} \\[0.2em] \lHat
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \XHat' \OHat^{-1} \XHat & R' \\
      R & 0
   \end{array} \right]^{-1} .
   \label{eq:cov-2sls-w2sls-3sls-r}
\end{equation}

The 3SLS-IV estimator restricted by $R \beta^R = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-IV} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \XHat' \OHat^{-1} X & R' \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \XHat' \OHat^{-1} y \\ q
   \end{array} \right] ,
   \label{eq:3slsIvR}
\end{equation}
where
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-IV} \\[0.2em] \lHat
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \XHat' \OHat^{-1} \XHat & R' \\
      R & 0
   \end{array} \right]^{-1} .
\end{equation}
The restricted 3SLS-GMM estimator can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-GMM} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' Z \left( Z' \OHat Z \right)^{-1} Z' X & R' \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' Z \left( Z \OHat Z \right)^{-1} Z' y \\ q
   \end{array} \right] ,
   \label{eq:3slsGmmR}
\end{equation}
where
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-GMM} \\[0.2em] \lHat
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' Z \left( Z' \OHat Z \right)^{-1} Z' X & R' \\
      R & 0
   \end{array} \right]^{-1} .
\end{equation}
The restricted 3SLS estimator based on the suggestion of
\cite{schmidt90} is
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-Schmidt} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \XHat' \OHat^{-1} \XHat & R' \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \XHat' \OHat^{-1} Z \left( Z' Z \right)^{-1} Z' y \\ q
   \end{array} \right] ,
   \label{eq:3slsSchmidtR}
\end{equation}
where
\begin{eqnarray}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-Schmidt} \\[0.2em] \lHat
   \end{array} \right] 
   & = & 
   \left[ \begin{array}{cc}
      \XHat' \OHat^{-1} \XHat & R' \\
      R & 0
   \end{array} \right]^{-1}
   \\
   & & \cdot
   \left[ \begin{array}{cc}
      \XHat' \OHat^{-1} Z \left( Z' Z \right)^{-1} Z' \OHat
      Z \left( Z' Z \right)^{-1} Z' \OHat^{-1} \XHat & 0' \\
      0 & 0
   \end{array} \right]^{-1}
   \nonumber \\
   & & \cdot
   \left[ \begin{array}{cc}
      \XHat' \OHat^{-1} \XHat & R' \\
      R & 0
   \end{array} \right]^{-1} .
   \nonumber
\end{eqnarray}
The econometrics software \proglang{EViews} calculates the restricted 3SLS estimator by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-EViews} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \XHat' \OHat^{-1} \XHat & R' \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \XHat' \OHat^{-1} \left( y - X \bHat^R_{2SLS} \right)
      \\ q 
   \end{array} \right] ,
   \label{eq:3slsEViewsR}
\end{equation}
where $\bHat^R_{2SLS}$ is the restricted 2SLS estimator calculated
by equation (\ref{eq:2sls-w2sls-3sls-r}).
\proglang{EViews} uses the standard formula of the restricted 3SLS
estimator~(\ref{eq:cov-2sls-w2sls-3sls-r}) to calculate an estimator
for the covariance matrix of the estimated coefficients.

>>>>

If the first method (Equation~\ref{eq:T-restr}) is chosen
to estimate the coefficients under these restrictions,
the matrix of regressors $X$ is (post-)\hspace{0pt}multiplied
by the $M$ matrix,
so that
\begin{equation}
    X^M = X \cdot M .
\end{equation}
Then, $X^M$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(Equations~\ref{eq:ols-wls-sur}--\ref{eq:3slsEViews}).
This results in the linear independent coefficient estimates $\bHat^M$ and
their covariance matrix.
The original coefficients can be obtained by Equation~\ref{eq:T-restr}
and the estimated covariance matrix of the original coefficients
can be obtained by
\begin{equation}
   \COVHat \left[ \bHat \right]
   = M \cdot \COVHat \left[ \bHat^M \right] \cdot M^\top .
\end{equation}

The implementation of the second method to estimate the coefficients
under linear restrictions (Equation~\ref{eq:restr-R})
is described for each estimation method in the following sections.

@@

The OLS, WLS, and SUR estimators restricted by $R \beta^R = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X^\top \OHat^{-1} X & R^\top \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X^\top \OHat^{-1} y \\ q
   \end{array} \right] ,
   \label{eq:ols-wls-sur-r}
\end{equation}
where $\lambda$ is a vector of the Lagrangean multipliers of the restrictions
and $\OHat$ is defined as in section~\ref{sec:Estimation-ols-wls-sur}.
An estimator of the covariance matrix of the estimated coefficients is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R \\[0.2em] \lHat
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X^\top \OHat^{-1} X & R^\top \\
      R & 0
   \end{array} \right]^{-1} .
   \label{eq:cov-ols-wls-sur-r}
\end{equation}

@@

The 2SLS, W2SLS, and standard 3SLS estimators
restricted by $R \beta^R = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \XHat^\top \OHat^{-1} \XHat & R^\top \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \XHat^\top \OHat^{-1} y \\ q
   \end{array} \right] ,
   \label{eq:2sls-w2sls-3sls-r}
\end{equation}
where $\OHat$ is defined as in section~\ref{sec:Estimation-2sls-w2sls-3sls}.
An estimator of the covariance matrix of the estimated coefficients is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R \\[0.2em] \lHat
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \XHat^\top \OHat^{-1} \XHat & R^\top \\
      R & 0
   \end{array} \right]^{-1} .
   \label{eq:cov-2sls-w2sls-3sls-r}
\end{equation}

The 3SLS-IV estimator restricted by $R \beta^R = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-IV} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \XHat^\top \OHat^{-1} X & R^\top \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \XHat^\top \OHat^{-1} y \\ q
   \end{array} \right] ,
   \label{eq:3slsIvR}
\end{equation}
where
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-IV} \\[0.2em] \lHat
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \XHat^\top \OHat^{-1} X & R^\top \\
      R & 0
   \end{array} \right]^{-1} .
\end{equation}
The restricted 3SLS-GMM estimator can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-GMM} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X^\top Z \left( Z^\top \OHat Z \right)^{-1} Z^\top X & R^\top \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X^\top Z \left( Z \OHat Z \right)^{-1} Z^\top y \\ q
   \end{array} \right] ,
   \label{eq:3slsGmmR}
\end{equation}
where
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-GMM} \\[0.2em] \lHat
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X^\top Z \left( Z^\top \OHat Z \right)^{-1} Z^\top X & R^\top \\
      R & 0
   \end{array} \right]^{-1} .
\end{equation}
The restricted 3SLS estimator based on the suggestion of
\cite{schmidt90} is
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-Schmidt} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \XHat^\top \OHat^{-1} \XHat & R^\top \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \XHat^\top \OHat^{-1} Z \left( Z^\top Z \right)^{-1} Z^\top y \\ q
   \end{array} \right] ,
   \label{eq:3slsSchmidtR}
\end{equation}
where
\begin{eqnarray}
   \COVHat
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-Schmidt} \\[0.2em] \lHat
   \end{array} \right] 
   & = & 
   \left[ \begin{array}{cc}
      \XHat^\top \OHat^{-1} \XHat & R^\top \\
      R & 0
   \end{array} \right]^{-1}
   \\
   & & \cdot
   \left[ \begin{array}{cc}
      \XHat^\top \OHat^{-1} Z \left( Z^\top Z \right)^{-1} Z^\top \OHat
      Z \left( Z^\top Z \right)^{-1} Z^\top \OHat^{-1} \XHat & 0^\top \\
      0 & 0
   \end{array} \right]^{-1}
   \nonumber \\
   & & \cdot
   \left[ \begin{array}{cc}
      \XHat^\top \OHat^{-1} \XHat & R^\top \\
      R & 0
   \end{array} \right]^{-1} .
   \nonumber
\end{eqnarray}
The econometrics software \proglang{EViews} calculates the restricted 3SLS estimator by
\begin{equation}
   \left[ \begin{array}{c}
      \bHat^R_{3SLS-EViews} \\[0.2em] \lHat
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \XHat^\top \OHat^{-1} \XHat & R^\top \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \XHat^\top \OHat^{-1} \left( y - X \bHat^R_{2SLS} \right)
      \\ q 
   \end{array} \right] ,
   \label{eq:3slsEViewsR}
\end{equation}
where $\bHat^R_{2SLS}$ is the restricted 2SLS estimator calculated
by Equation~\ref{eq:2sls-w2sls-3sls-r}.
\proglang{EViews} uses the standard formula of the restricted 3SLS
estimator (Equation~\ref{eq:cov-2sls-w2sls-3sls-r}) to calculate an estimator
for the covariance matrix of the estimated coefficients.
